Altering Backward Pass Gradients\\ to Improve Convergence

### 2022-11-21 0100.tex
Mod7

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{framed}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{url}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\graphicspath{{images/}}
\raggedbottom
\newcommand{\forceindenta}{\parindent=1em\indent\parindent=0pt\relax}
\newcommand{\forceindentb}{\parindent=1.65em\indent\parindent=0pt\relax}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\NewDocumentCommand{\codeword}{v}{\texttt{\textcolor{orange}{#1}}}
\newcommand{\cmark}{\ding{51}} \newcommand{\xmark}{\ding{55}}
\definecolor{newcolor}{rgb}{.8,.349,.1}
\definecolor{codegreen}{rgb}{0.7,0.7,0.7}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{1,1,1}
\lstdefinestyle{mystyle}{ backgroundcolor=\color{backcolour},   
commentstyle=\color{codegreen}, keywordstyle=\color{magenta},
numberstyle=\tiny\color{codegray}, stringstyle=\color{codepurple},
basicstyle=\ttfamily\footnotesize, breakatwhitespace=false,         
breaklines=true,                 
captionpos=b,                    
keepspaces=true,                 
numbersep=5pt,                  
showspaces=false,                
showstringspaces=false, showtabs=false,                  
tabsize=2 }
\lstset{style=mystyle}

\begin{document}
\title{Altering Backward Pass Gradients to improve Convergence}
\author{Bishshoy Das\inst{1}\orcidID{0000-0002-6525-4015}\and Milton Mondal\inst{1}\orcidID{xxxx-xxxx-xxxx-xxxx}\and Brejesh Lall\inst{3}\orcidID{xxxx-xxxx-xxxx-xxxx}\and Shiv Dutt Joshi\inst{3}\orcidID{0000-0002-0326-0524}\and Sumantra Dutta Roy\inst{3}\orcidID{0000-0002-2141-5067}}
\authorrunning{Das et al.}
\institute{Indian Institute of Technology Delhi, New Delhi - 110016, India \\ \email{\{bishshoy.das, milton.mondal, brejesh, sdjoshi, sumantra\}@ee.iitd.ac.in}}
\maketitle

@@

@@

\subsection{Norm plots of weights (baseline (low batch size)) of non-BN ResNet-18}
\label{sec:plots1}
\begin{figure}[ht] \centering \includegraphics[width=0.57\textwidth]{baseline-w_norm}
\caption{ Method: baseline, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. Readers are requested to zoom in. } \end{figure}

@@

\subsection{Norm plots of weights (baseline (high batch size)) of non-BN ResNet-18}
\label{sec:plots2}
\begin{figure}[ht] \centering
\includegraphics[width=0.57\textwidth]{baseline_high_bs-w_norm} \caption{ Method:
baseline (high batch size), batch size = 1024. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. Readers are requested to zoom in. } \end{figure}

@@

\subsection{Norm plots of weights (PGT) of non-BN ResNet-18}
\label{sec:plots3}
\begin{figure}[ht] \centering \includegraphics[width=0.57\textwidth]{pgt-w_norm}
\caption{ Method: PGT, batch size = 256. This is a plot depicting the iteration-wise
evolution of the norm of each filter in each layer. Each subplot corresponds to a layer
of the unnormalized ResNet-18. Above each subplot, the layer indices are shown. Each
filter in each subplot is shown with a separate and randomly determined colour. Readers
are requested to zoom in. }
\end{figure}

@@

\subsection{Norm plots of weights (AGC + PGT) of non-BN ResNet-18}
\label{sec:plots4}
\begin{figure}[ht] \centering \includegraphics[width=0.57\textwidth]{agc_pgt-w_norm}
\caption{ Method: AGC + PGT, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour.
Readers are requested to zoom in. } \end{figure}

>>>>

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{framed}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{url}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\graphicspath{{images/}}
\raggedbottom
\makeatletter
\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother
\newcommand{\forceindenta}{\parindent=1em\indent\parindent=0pt\relax}
\newcommand{\forceindentb}{\parindent=1.65em\indent\parindent=0pt\relax}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\NewDocumentCommand{\codeword}{v}{\texttt{\textcolor{orange}{#1}}}
\newcommand{\cmark}{\ding{51}} \newcommand{\xmark}{\ding{55}}
\definecolor{newcolor}{rgb}{.8,.349,.1}
\definecolor{codegreen}{rgb}{0.7,0.7,0.7}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{1,1,1}
\lstdefinestyle{mystyle}{ backgroundcolor=\color{backcolour},   
commentstyle=\color{codegreen}, keywordstyle=\color{magenta},
numberstyle=\tiny\color{codegray}, stringstyle=\color{codepurple},
basicstyle=\ttfamily\footnotesize, breakatwhitespace=false,         
breaklines=true,                 
captionpos=b,                    
keepspaces=true,                 
numbersep=5pt,                  
showspaces=false,                
showstringspaces=false, showtabs=false,                  
tabsize=2 }
\lstset{style=mystyle}

\begin{document}
\title{Altering Backward Pass Gradients\\ to Improve Convergence}
\author{Bishshoy Das\inst{\ast 1}\orcidID{0000-0002-6525-4015}\and Milton Mondal\inst{\ast 1}\orcidID{0000-0002-1832-0702}\and Brejesh Lall\inst{1}\orcidID{0000-0003-2677-3071}\and Shiv Dutt Joshi\inst{1}\orcidID{0000-0002-0326-0524}\and Sumantra Dutta Roy\inst{1}\orcidID{0000-0002-2141-5067}}
\authorrunning{Das et al.}
\institute{Indian Institute of Technology Delhi, New Delhi - 110016, India \\ \email{\{bishshoy.das, milton.mondal, brejesh, sdjoshi, sumantra\}@ee.iitd.ac.in}}
\maketitle

@@

\blfootnote{$^\ast \text{Equal contribution.}$}

@@

\subsection{Norm plots of weights (baseline (low batch size)) of non-BN ResNet-18}
\label{sec:plots1}
\begin{figure}[ht]
\centering
\includegraphics[width=0.57\textwidth]{compressed/baseline-w_norm}
\caption{ Method: baseline, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour. Readers are requested to zoom in. } 
\end{figure}

@@

\subsection{Norm plots of weights (baseline (high batch size)) of non-BN ResNet-18}
\label{sec:plots2}
\begin{figure}[ht]
\centering
\includegraphics[width=0.57\textwidth]{compressed/baseline_high_bs-w_norm}
\caption{ Method: baseline (high batch size), batch size = 1024. This is a plot
depicting the iteration-wise evolution of the norm of each filter in each layer. Each
subplot corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the
layer indices are shown. Each filter in each subplot is shown with a separate and
randomly determined colour. Readers are requested to zoom in. } \end{figure}

@@

\subsection{Norm plots of weights (PGT) of non-BN ResNet-18}
\label{sec:plots3}
\begin{figure}[ht]
\centering
\includegraphics[width=0.57\textwidth]{compressed/pgt-w_norm}
\caption{ Method: PGT, batch size = 256. This is a plot depicting the iteration-wise
evolution of the norm of each filter in each layer. Each subplot corresponds to a layer
of the unnormalized ResNet-18. Above each subplot, the layer indices are shown. Each
filter in each subplot is shown with a separate and randomly determined colour. Readers
are requested to zoom in. }
\end{figure}

@@

\subsection{Norm plots of weights (AGC + PGT) of non-BN ResNet-18}
\label{sec:plots4}
\begin{figure}[ht]
\centering
\includegraphics[width=0.57\textwidth]{compressed/agc_pgt-w_norm}
\caption{ Method: AGC + PGT, batch size = 256. This is a plot depicting the
iteration-wise evolution of the norm of each filter in each layer. Each subplot
corresponds to a layer of the unnormalized ResNet-18. Above each subplot, the layer
indices are shown. Each filter in each subplot is shown with a separate and randomly
determined colour.
Readers are requested to zoom in. }
\end{figure}
